---
title: "readMe"
author: "Elizabeth Permina"
date: "1/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## RISmed

RISmed is a package to extract data from PUBMED and parse the output. It has functions to process authors, title, abstract, etc. I'm looking for ways of extracting the reference list (which is a part of extracted xml record). Issue - I didn't find a way to parse it yet. The xml record of the reference list is highly nested and has a lot of repeating tags, so xml to dataframe functions don't work (columns with the same name error)

XML package effectively translates full pubmed xml (with references) into a list with 1) non-unique names of variables 2) nested names like
```{r, eval=FALSE}
$PubmedArticle$PubmedData$ReferenceList$Reference$ArticleIdList
$PubmedArticle$PubmedData$ReferenceList$Reference$ArticleIdList$ArticleId
$PubmedArticle$PubmedData$ReferenceList$Reference$ArticleIdList$ArticleId$text
$PubmedArticle$PubmedData$ReferenceList$Reference$ArticleIdList$ArticleId$.attrs
  IdType 
"pubmed" 
$PubmedArticle$PubmedData$ReferenceList$Reference$PubmedArticle$PubmedData$ReferenceList$Reference$Citation
```

corresponding xml looks like that
88dc43de-71be-11ec-8542-d21848e7cc81.xml
to get an xml file out of PMID id (one by one)
https://pubmed2xl.com/xml/
